MLH1 Results Outline

### 2020-04-28 doc/Results_v2.rmd
IFD figure drafts knited into html results draft

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
library(patchwork)
library(pander)
library("xlsx")

@@

```{r triangle.IFD.auto.loop.ifd, echo=FALSE, eval=FALSE}

#Top is female
top.triangle2 <- function() {
  #top-y position is male Pos2
  plot(  (Curated_BivData %>% filter(strain == "WSB"  ) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2 ~ 
    #top-x position is female Pos1     
    (Curated_BivData %>% filter(strain == "WSB"   ) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_1,

       data= (Curated_BivData %>% filter(sex == "female") %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2) ), 
       col =  colors_of_strains["WSB"],
       axes=FALSE, ylab='', xlab="", 
       main= "IFD Distribution",  xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1)

  mtext("WSB", 3, 5, font=2, cex=1.3, adj=.5)
  mtext("Female Position.2", 2, .75)
  mtext("Female Position.1", 3, 2)
  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
  }

bottom.triangle2 <- function() {
    #bottom-y position is male Pos1
  points(  (Curated_BivData %>% filter(strain == "WSB") %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_1 ~ 
    #bottom-x position is male Pos2     
    (Curated_BivData %>% filter(strain == "WSB") %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_2,

         data=(Curated_BivData %>% filter(sex == "male") %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2) ),

    col =  colors_of_strains["WSB"], xpd=TRUE)
  mtext("Male Position.2", 1, 1.5, at=mean(par()$usr[1:2])) #  + x.dist
  mtext("Male Position.1", 4, 3)#, padj=par()$usr[1]
  x.at <- axisTicks(par()$usr[1:2], 0) #+ x.dist
  axis(side=1, las=1, pos=0, at=x.at, labels=F, xpd=TRUE)
  mtext(seq(0, 1, .2), 1, 0, at=x.at)
  axis(4, las=1, pos=1) # + x.dist
  lines(0:1, 0:1, xpd=TRUE)# + x.dist
  }

#par(mar=c(1,1,1,1))
op <- par(mar=c(3, 4, 8, 12) + 0.1, oma=c(2, 0, 0, 2))
plot(top.triangle2(), bottom.triangle2() ) #not working
par(op)
dev.off()

```{r double.tri.rewrite, fig.width = 6.5, fig.height=5}

@@

#this works
top.triangle2 <- function(my.y, my.x, my.data) {
  plot(my.y ~ my.x, data= my.data, axes=FALSE, ylab='', xlab="", 
       main='', xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1,
       col =  colors_of_strains[current.strain])
  mtext(current.strain, 3, 5, font=2, cex=1.3, adj=.95)
  mtext("Position.2.Female", 2, .75)
  mtext("Position.1.Female", 3, 2)
  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
}

@@

x.dist <- .5
RP <- list()

@@

  #declare file for saving png
  #png(paste0("~./MLH1repo/doc/figureFiles/test.triangle_", current.strain, ".png"),  width=650, height=500)
  plot.new()

@@

  op <- par(mar=c(3, 4, 8, 12) + 0.1, oma=c(2, 0, 0, 2))

@@

  #try recordPlot(),

  #x.plot.list[[i]] <- function(){top.triangle2(my.y.top, my.x.top, my.data)}
  #x.plot.list.b[[i]] <- function(){top.triangle2(my.y.top, my.x.top, my.data), bottom.triangle2(my.y.bottom+x.dist, my.x.bottom, my.data)}
  # p <- recordPlot()
  #grid.echo()
  #a <- grid.grab()

@@

#for(ee in 1:7){
#  #print(ee)
#  RP[[ee]]
#  plot.new()
#}

@@

library(png)

#load all the files / arrange the plots from above 
WSB.triangle.png <- readPNG("~./MLH1repo/doc/figureFiles/test.triangle_WSB.png")

#make empty DF for ggplot object
empty.DF <- data.frame(col1 = c(1,3), col2 = c(1,3) )

#make an empty ggplot thing, then background ontop
WSB.triangle.ggplot <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(WSB.triangle.png) + theme(axis.title.x=element_blank(),
 axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

#show wsb as example
WSB.triangle.ggplot

#library("cowplot")
#fig1  <- ggdraw() +
#  draw_plot(WSB.triangle.ggplot, x=0, y=0, width=.45, height=.45) +
#  draw_plot(G.triangle.ggplot,   x=0, y=.4, width=.45, height=.45) +
#  draw_plot(LEW.triangle.ggplot, x=0, y=.6, width=.45, height=.45)

#ggsave("~./WildMiceMadison/results/Figure1.png")
```

@@

```{r Q1.IFD.plot, echo=FALSE}

#make interference plots of IFD, position p1 by p2

@@

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
library(patchwork)
library(pander)
library("xlsx")
library(png)
#library(tidyverse)
library(png)
library(grid)
library(gridBase)
library(gridExtra)
library(dplyr)
library(cowplot)

@@

```{r double.tri.rewrite, echo=FALSE}

@@

#this works
top.triangle2 <- function(my.y, my.x, my.data) {
  plot(my.y ~ my.x, data= my.data, axes=FALSE, ylab='', xlab="", 
       main='', xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1,
       col =  colors_of_strains[current.strain])

  mtext(current.strain, 3, 5, font=2, cex=1.3, adj=.95)
  mtext("Position.2.Female", 2, .75)
  mtext("Position.1.Female", 3, 2)

  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
}

@@

x.dist <- .25
RP <- list()

@@

  #declare file for saving png
  png(paste0("~./MLH1repo/doc/figureFiles/IFD.triangle_", current.strain, ".png"),  width=650, height=500, res=100)

  plot.new()

@@

  #adjusting this mar lowers the margins
  op <- par(mar=c(1.5, 2, 4, 6) + 0.1, oma=c(2, 0, 0, 2))

@@

@@

#testing <- plot_grid( rasterGrob(RP[[1]]), rasterGrob(RP[[2]]), rasterGrob(RP[[3]]),
#                   rasterGrob(RP[[4]]), rasterGrob(RP[[5]]), rasterGrob(RP[[6]]),
#                   rasterGrob(RP[[7]]),                     labels="AUTO")
#ggsave(filename = "~./MLH1repo/doc/figureFiles/test.triangle_all.png", plot = testing, 
#       width = 10, height = 10)

@@

plot1.WSB <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_WSB.png')
plot2.LEW <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_LEW.png')
plot3.G <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_G.png')

plot4.KAZ <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_KAZ.png')
plot5.SKIVE <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_SKIVE.png')
plot6.PWD <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_PWD.png')

plot7.MSM <- readPNG('~/MLH1repo/doc/figureFiles/IFD.triangle_MSM.png')

grid.arrange(rasterGrob(plot1.WSB), rasterGrob(plot2.LEW), rasterGrob(plot3.G),
             rasterGrob(plot4.KAZ), rasterGrob(plot5.SKIVE), rasterGrob(plot6.PWD),
             rasterGrob(plot7.MSM), 
             ncol=3)

#load all the files / arrange the plots from above 
#WSB.triangle.png <- readPNG("~./MLH1repo/doc/figureFiles/test.triangle_WSB.png")

@@

@@

```{r Q2.double.tri.rewrite, echo=FALSE}
#choose the categories to compare 
#all male strains
#just bottom triangles?

#good function, saves to file, can't reproduce in rmd ..width=650, height=500
#big loop for automating the IFD triangles
Q2.males.IFD <- c("F1", "other")
Q2.auto_curate_DF <- Curated_BivData[ ! Curated_BivData$strain %in% Q2.males.IFD, ]

Q2.df_strain_list <- split(Q2.auto_curate_DF, (Q2.auto_curate_DF$strain))
Q2.df_strain_list <- Q2.df_strain_list[ -c(4,10,11,12,13,14,15,16,17,18,19) ]

#this works
Q2.bottom.triangle2 <- function(my.y, my.x, my.data){
  points(my.x ~ my.y, data=my.data, xpd=TRUE, 
          col =  colors_of_strains[current.strain])

  mtext("Position.2.Male", 1, 1.5, at=mean(par()$usr[1:2]))
  mtext("Position.1.Male", 4, 3, padj=par()$usr[1] +4)
  x.at <- axisTicks(par()$usr[1:2], 0)
  axis(side=1, las=1, pos=0, at=x.at, 
       labels=F, xpd=TRUE)
  mtext(seq(0, 1, .2), 1, 0, at=x.at)
  axis(4, las=1, pos=1)
  lines(0:1, 0:1, xpd=TRUE)
}

#figure out to move up the bottom axis text

x.dist <- .25
RP <- list()

for(i in 1:(length(Q2.df_strain_list))){
  #print(i)
  current.strain <- as.character(Q2.df_strain_list[[i]]$strain[1])

  #declare file for saving png
  png(paste0("~./MLH1repo/doc/figureFiles/Q2.IFD.triangle_", current.strain, ".png"),  width=650, height=500, res=100)
  plot.new()

  my.data = (Curated_BivData %>% filter(strain == current.strain) %>% filter(hand.foci.count == 2) )
  my.x.bottom = (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_1 
  my.y.bottom = (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_2

  #adjusting this mar lowers the margins
  op <- par(mar=c(1.5, 2, 4, 6), oma=c(2, 0, 0, 2))

  Q2.bottom.triangle2(my.y.bottom, my.x.bottom, my.data) #x.dist

```{r Q2.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE}

Q2.plot1.WSB <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_WSB.png')
Q2.plot2.LEW <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_LEW.png')
Q2.plot3.G <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_G.png')

Q2.plot4.KAZ <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_KAZ.png')
Q2.plot5.SKIVE <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_SKIVE.png')
Q2.plot6.PWD <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_PWD.png')

Q2.plot7.MSM <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_MSM.png')
Q2.plot8.MOLF <- readPNG('~/MLH1repo/doc/figureFiles/Q2.IFD.triangle_MOLF.png')

grid.arrange(rasterGrob(Q2.plot1.WSB), rasterGrob(Q2.plot2.LEW), rasterGrob(Q2.plot3.G),
             rasterGrob(Q2.plot4.KAZ), rasterGrob(Q2.plot5.SKIVE), rasterGrob(Q2.plot6.PWD),
             rasterGrob(Q2.plot7.MSM), rasterGrob(Q2.plot8.MOLF), 
             ncol=3)
